\papertitle

### 2021-03-04 source_separation/paper/paper.tex
Edit abstract

	\begin{abstract}
		The abstract should be placed at the top left column and should contain about 150-200 words.
	\end{abstract}
	%

@@

@@

>>>>

	\begin{abstract}
		In this paper, we will study the possibility of adding source separation as a pre-processing step to the orchestration process. We first discuss the motivation of this addition and its effect on the quality of orchestrations of multi-layered sounds. Second, we select several state-of-the-art models for both music source separation (separation of instruments) and universal sound separation (separation of arbitrary sounds of different types), and compare their effectiveness for the task of orchestration. By applying these methods to hand picked target sounds, then orchestrating the separated outputs, and finally comparing them to the orchestration of the same target without separation, we can determine which methods best suit the needs of orchestration. Our experiments show that the quality of orchestrations improved, both qualitatively and quantitatively, indicating that our approach is promising. Finally, we discuss the interest of unsupervised methods compared to supervised methods in the case of assisted orchestration, where data is relatively scarce.
	\end{abstract}
	%

@@

	 In the field of computer-assisted composition, musical orchestration is probably the most empirical one and it has been traditionally taught in an intuitive and non formalized way. Computer-assisted orchestration seeks to help composers by accelerating certain creative processes. In particular, target-based computer-assisted orchestration helps composers to explore new timbral possibilities by associating instrumental samples, which, combined, will sound perceptually similar to a target sound. \textbf{(Note: This paragraph was moved to the intro from the abstract. We can move it back to the abstract if that would be better)}

@@

			OpenUnmix \cite{open-unmix}
